The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-17 paper/ms.tex
added variability analysis
hedge

We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp < 1$, we identify 64 of these objects as evolved systems, and the remaining~38 lie apparently on the main sequence.

>>>>

We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp < 1$, we identify 64 of these objects as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.
